gazeHMM: Parameter recovery simulation

### 2020-05-09 simulation/preregistration_parameter_recovery.Rmd
update parameter recovery

In the second part, we will vary the sample size of the generated data and the amount of noise added to it. The model parameters will be set to their fixed values. For models with $k \in \{2, 3, 4\}$ states and sample sizes of $N \in \{500, 2500, 10000\}$, we will generate 100 data sets ($100 \times 3 \times 3 = 900$ recoveries). We chose samples sizes roughly corresponding to small, medium, and large eye-tracking data sets of a single participant and trial. To simulate measurement error, we will add Gaussian white noise with $\mu = 0$ and $\sigma \in [1,5]$ varying between data sets to velocity and acceleration. Values that decrease to zero or below will be set to 0.001. We will add white noise from a von-Mises distribution with $\mu = 0$ and $\kappa \in 1/[0.1,10]$ varying between data sets to angle.

@@

In the last part, we will set intervals of the generated data to be missing. The model parameters will be set to the fixed values. For $k \in \{2, 3, 4\}$ states and $n_{miss} \in \{1, 3, 5\}$ intervals, 100 data sets with $N = 2500$ samples will be generated ($100 \times 3 \times 3 = 900$ recoveries). The size of the missing data interval $m \in [1,250]$ samples will vary between the data sets.

@@

@@

>>>>

In the second part, we will vary the sample size of the generated data and the amount of noise added to it. The model parameters will be set to their fixed values. For models with $k \in \{2, 3, 4\}$ states and sample sizes of $N \in \{500, 2500, 10000\}$, we will generate 100 data sets ($100 \times 3 \times 3 = 900$ recoveries). We chose samples sizes roughly corresponding to small, medium, and large eye-tracking data sets of a single participant and trial. To simulate measurement error, we will add Gaussian white noise with $\mu = 0$ and $\sigma \in [1,5]$ varying between data sets to velocity and acceleration. Values that decrease to zero or below will be set to 0.001. To angle, we will add white noise from a von-Mises distribution with $\mu = 0$ and $\kappa \in 1/[0.1,10]$ varying in equidistant steps between data sets.

@@

In the last part, we will set intervals of the generated data to be missing. The model parameters will be set to the fixed values. For $k \in \{2, 3, 4\}$ states and $n_{miss} \in \{1, 3, 5\}$ intervals, 100 data sets with $N = 2500$ samples will be generated ($100 \times 3 \times 3 = 900$ recoveries). The size of the missing data interval $m \in [1,250]$ samples will vary in equidistant steps between the data sets.

@@

When a model can not be fitted to a data set, it will be excluded from the recovery. We expect at least 95% of all models to be fitted.

***

@@

***
